---
title: "Assignment3_FML"
author: "Karthik Badiganti"
date: "2022-10-13"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages

```{r packages}

library(class)
library(caret)
library(ISLR)
library(tidyverse)
library(knitr)
library(e1071)
library(gmodels)
library(ggplot2)
library("pROC")
```

## Data Preparation
### Data Preparation{.tabset}
#### Importing & Cleaning Data {.tabset}

We are Importing Data from CSV file and cleaning

```{r import and clean Data}


Universal_bank <- read.csv("C://Users//gbkar//Documents//R Scripts//UniversalBank.csv")



#Making decision variable into factor as it is a classification model
Universal_bank$Personal.Loan<-as.factor(Universal_bank$Personal.Loan)


#Removing unnecessary variables and rearranging the variable as per test data
Universal_bank <-Universal_bank[,c("Personal.Loan","Online","CreditCard")]


# Converting Categorical Variables to Factors
Universal_bank$Online<-as.factor(Universal_bank$Online)
Universal_bank$CreditCard<-as.factor(Universal_bank$CreditCard)
head(Universal_bank)

```

#### Data Partition and Normalization

```{r Data Partition and Normalization}

set.seed(133)
#Partitioning Data into 60% Training and 40% Validation
Index_Train<-createDataPartition(Universal_bank$Personal.Loan, p=0.6, list=FALSE)

Universal_bank_Train <-Universal_bank[Index_Train,]

Universal_bank_Validation  <-Universal_bank[-Index_Train,]
print(paste("No. of rows in Train data is",nrow(Universal_bank_Train)))
print(paste("No. of rows in Validation data is",nrow(Universal_bank_Validation)))

```
$$\text{We are skipping normalization as there are only categorical variables}$$


## A & B. Pivot Table and Direct Calculation 


### A. Online with CreditCard & Personal.Loan 

Building a Pivot Table with Online as column variable and Credit Card as Row Variable Along with Loan as Secondary row variable.
```{r pivot1}

pivot1<-ftable(Universal_bank_Train$Online,Universal_bank_Train$CreditCard,Universal_bank_Train$Personal.Loan, row.vars = c(3,2),dnn=c('Online','CreditCard','Personal.loan'))

print("Pivot Table for the given variables is")
pivot1
     
```



### B. Probability of Loan Given CC and Online

```{r Probability of Loan Given CC and Online}
# Pivot Table from question A
P1<- pivot1[4,2]/(pivot1[2,2]+pivot1[4,2])

```

$$   P(\frac{Loan=1}{CC=1,Online=1})
=\frac{45}{45+475}=  0.0865384615384615\\
Probability\hspace{.3cm} is \hspace{.3cm} 0.0865384615384615$$



## C,D,E. Pivot Tables and Naive Bayes 

### C. Online with Loan & Credit Card with Loan{.tabset}
#### Online with Loan


```{r pivot2}
pivot2<-ftable(Universal_bank_Train$Online, Universal_bank_Train$Personal.Loan,
       row.vars = c(2),dnn=c('Online', 'Personal.loan'))
print("Pivot Table for the given variables is")
pivot2
     
```

#### CreditCard with Loan


```{r pivot3}
pivot3<-ftable(Universal_bank_Train$CreditCard, Universal_bank_Train$Personal.Loan,
       row.vars = c(2),dnn=c('CreditCard', 'Personal.loan'))
print("Pivot Table for the given variables is")
pivot3     
```

### D.Caculations Based on Pivot Tables


#### Individual Probabilities
##### Probabilities CC Given Loan{.tabset}
###### Probability of CC 1 given Loan 1

```{r Probability of CC 1 given Loan 1}
pivot3
P2<- pivot3[2,2]/(pivot3[2,1]+pivot3[2,2])
P2
```


###### Probability of CC 1 given Loan 0
```{r Probability of CC 1 given Loan 0}
pivot3
P3<- pivot3[1,2]/(pivot3[1,1]+pivot3[1,2])
P3
```
##### Below Are the results
$$   P(\frac{CC=1}{Loan=1})
=\frac{79}{209+79}=  0.2743056\\$$
$$   P(\frac{CC=1}{Loan=0})
=\frac{794}{1918+794}=   0.2927729\\$$

##### Probabilities Online Given Loan{.tabset}
###### Probability of Online 1 given Loan 1
```{r Probability of Online 1 given Loan 1}
pivot2
P4<- pivot2[2,2]/(pivot2[2,1]+pivot2[2,2])
P4
```

###### Probability of Online 1 given Loan 0
```{r Probability of Online 1 given Loan 0}
pivot2
P5<- pivot2[1,2]/(pivot2[1,1]+pivot2[1,2])
P5
```
##### Below Are the results
$$   P(\frac{Online=1}{Loan=1})
=\frac{182}{106+182}=  0.6319444\\$$
$$   P(\frac{Online=1}{Loan=0})
=\frac{1584}{1128+1584}=   0.5840708\\$$

##### Probability of Loan
```{r Probability of Loan 0, Loan 1}
P6<-(filter(Universal_bank_Train,Personal.Loan==1) %>%count())/nrow(Universal_bank_Train)
P6<-P6[[1]]

P7<-(filter(Universal_bank_Train,Personal.Loan==0) %>%count())/nrow(Universal_bank_Train)
P7<-P7[[1]]
P6
P7
```
$$   P({Loan=1})
=\frac{288}{3000}=  0.096\\$$
$$   P({Loan=0})
=\frac{2712}{3000}=   0.904\\$$

### E. Naive Bayes

```{r Naive Bayes}
P8 <- (P2*P4*P6)/((P2*P4*P6)+(P3*P5*P7))
P8

```
$$  Naive Bayes = P(\frac{Loan=1}{CC=1,Online=1}) = 
\frac{P(\frac{CC=1}{Loan=1})P(\frac{Online=1}{Loan=1})P(Loan=1)}
{P(\frac{CC=1}{Loan=1})P(\frac{Online=1}{Loan=1})P(Loan=1)+P(\frac{CC=1}{Loan=0})P(\frac{Online=1}{Loan=0})P(Loan=0)}\\=0.09718894\\
\text{Naive Bayes Probability is} \hspace{.3cm} 0.09718894$$

## F. Comparision

### Comparision b/w Naive bayes probability and Probability Using Pivot Table
```{r Comparision b/w Naive and Pivot}
P8-P1

```

$$\text{The Probability obtained using pivot table is 0.0865384615384615. }\\
\text{The Probability obtained using Naive bayes formula is 0.09718894. }\\
\text{Since in Naive Bayes, We assume conditional independence.}\\
\text{Hence, there is an increase of 0.01065048 in the value of probability }
$$

## G. Naive Bayes using R

```{r Naive Bayes using R}
# Creating Naive Bayes Classifier
Loan.prob <- naiveBayes(Personal.Loan ~ ., data = Universal_bank_Train) 

c(Loan.prob$apriori[1]/(Loan.prob$apriori[1]+Loan.prob$apriori[2]),Loan.prob$apriori[2]/(Loan.prob$apriori[1]+Loan.prob$apriori[2]))
Loan.prob$tables
```

$$\text{Since the individual probabilities are matching to the above calculations in Question. D.}\\
\text{Naive bayes probability=0.09718894}$$

### Roc Calculation and plot
```{r roc}


## predict probabilities
pred.prob <- predict(Loan.prob, newdata = Universal_bank_Validation, type = "raw")

###roc plot

roc(Universal_bank_Validation$Personal.Loan,pred.prob[,2])
plot.roc(Universal_bank_Validation$Personal.Loan,pred.prob[,2])

```
