---
title: "FMl Assignment 4"
author: "Karthik Badiganti"
date: "2022-11-03"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages

```{r packages}

library(caret)
library(dplyr)
library(ggplot2)
library(ISLR)
library(tidyverse)
library(factoextra)
library(cluster)
library(ggpubr)
library(FactoMineR)
library(gridExtra)
library(ggcorrplot)
library(esquisse)
```

## Data Preparation

### Data Preparation {.tabset}

#### Importing & Cleaning Data

We are Importing Data from CSV file and cleaning

```{r import and clean Data}


 pharmaceuticals <- read.csv("C://Users//gbkar//Documents//R Scripts//pharmaceuticals.csv")



# removing variables that are not required
pharma_k <-pharmaceuticals[,c(1,3,4,5,6,7,8,9,10,11)]

head(pharma_k)

```

#### Normalization

```{r normalization}
set.seed(123)

# Using center, scale for normalization of all the variables
norm_data <- preProcess(pharma_k[-1],method=c("center",'scale'))
pharma_norm<-predict(norm_data,pharma_k[-1])
head(pharma_norm)

```

We are normalizing data using center scale method as each variable has different units

## A. K-Means

### K selection

```{r k selection}
set.seed(23)
wss<-fviz_nbclust(pharma_norm[-1], kmeans, method = "wss",k.max=7)
silhouette<-fviz_nbclust(pharma_norm[-1], kmeans, method = "silhouette",k.max=7)
grid.arrange(wss,silhouette)
```

### K means

```{r k means}
set.seed(23)
rownames(pharma_k)<- pharma_k[[1]]
# From silhouette method K=3
k3 <- kmeans(pharma_norm[-1], centers = 3, nstart = 25)

# From WSS method elbow k=2
k2 <- kmeans(pharma_norm[-1], centers = 2, nstart = 25)

K31<-fviz_cluster(k3, data=pharma_k[-1],main='Based on Silhoutte K=3')
K21<-fviz_cluster(k2, data=pharma_k[-1],main='Based on WSS K=2')
grid.arrange(K21,K31)
 
```

Based on the above plots we can assume K=3 has better clustering than k=2 as we can study properties of clusters more clearly with K=3

### plots

```{r plot}
rownames(pharma_k)<- pharma_k[[1]]
fviz_cluster(k3, data=pharma_k[-1])
```

## B. Interpret Clusters with Variables Used

### Clusters

```{r Analysis}
clusters_pharma<-pharma_k %>% mutate(Cluster = k3$cluster)
s1<-as.list(clusters_pharma %>%filter(Cluster==1)%>% select(cluster1=Symbol) )
s2<-as.list(clusters_pharma %>%filter(Cluster==2)%>% select(cluster2=Symbol) )
s3<-as.list(clusters_pharma %>%filter(Cluster==3)%>% select(cluster3=Symbol) )
s<-as.data.frame(paste(s1[[1]],collapse = ' '))
s<-rbind(s,paste(s2[[1]],collapse = ' '))
s<-rbind(s,paste(s3[[1]],collapse = ' '))
rownames(s)<-c('cluster1','cluster2','cluster3')
colnames(s)<-'Firms Symbol'

# Clusters Formed by K means
s

```

### Analysis

```{r clusters}
clusplot(pharma_k,k3$cluster, main="Clusters",color = TRUE, labels = 2,lines = 0)
c1<-clusters_pharma[-1]%>% group_by(Cluster)%>% summarise_all('mean')
c1
```

From the above data, we can say that in

cluster 2 -\> high market cap average, high ROE average

cluster1-\> medium market cap average, low ROE average

cluster3 -\> low market cap average, medium ROE average

Similarly with the other variables

## C. Pattern with variables 10 to 12

```{r pattern c}
pharma_c<-pharmaceuticals[,c(12,13,14)]
pharma_c$cluster<-as.factor(clusters_pharma$Cluster)
```

### Bar plots with respect to other 3 variables {.tabset}

#### Clusters vs Exchange

```{r exchange}
ggplot(pharma_c) +
 aes(x = cluster, fill = Exchange, colour = Exchange, group = Exchange) +
 geom_bar(position = "dodge") +
 scale_fill_brewer(palette = "Accent", direction = 1) +
 scale_color_brewer(palette = "Accent", direction = 1) +
 theme_minimal()
```

From the graph, we can assume that the cluster grouping done based on the Exchange 'NYSE' with high medium and low with clusters 2,3,1 respectively

#### Clusters vs Median Recommendation

```{r median}
ggplot(pharma_c) +
 aes(x = cluster, fill = Median_Recommendation, colour = Median_Recommendation, group = Median_Recommendation) +
 geom_bar(position = "dodge") +
 scale_fill_brewer(palette = "Accent", direction = 1) +
 scale_color_brewer(palette = "Accent", 
 direction = 1) +
 theme_minimal()
```

From the graph, we can assume that the cluster grouping done based on the median recommendation 'Hold' with high medium and low with clusters 2,1,3 respectively

#### Clusters vs Location

```{r location}

ggplot(pharma_c) +
 aes(x = cluster, fill = Location, colour = Location, group = Location) +
 geom_bar(position = "dodge") +
 scale_fill_brewer(palette = "Accent", direction = 1) +
 scale_color_brewer(palette = "Accent", direction = 1) +
 theme_minimal()


```

From the graph, we can assume that the cluster grouping done based on the Location 'US' with high medium and low with clusters 2,3,1 respectively

### Summarize

From the above plots we assume that cluster 2 is grouped based on high count of one of the category in each of the variables and cluster 3 with medium count and cluster 1 has low count of categorical count.

## D. Appropriate Names to Clusters

Based on the Median recommendation graph we can say that

Cluster 1: New buyers

Cluster2: Experienced Traders

Cluster3: Resellers
